\texttt{SuperScreen}: An open-source package for simulating the magnetic response of two-dimensional superconductors

### 2021-09-17 main.tex

Once the stream function $\mathbf{g}$ is known for the full mesh,
the sheet current flowing in the film can be computed from Eq.~\ref{eq:stream}, the $z$-component of the total field in the plane of the film can be computed
from Eq.~\ref{eq:field_from_kernel_num}, and the full vector magnetic field $\vec{H}(x, y, z)$
at any point in space can be computed from Eq.~\ref{eq:field_from_kernel}.

@@

A \inline{superscreen.Parameter} is a wrapper around a Python function that computes a scalar value as a function of position coordinates ($x$, $y$, and optionally $z$) based on some set of keyword arguments. Addition, subtraction, multiplication, division, and exponentiation between \inline{Parameters}, other \inline{Parameters}, and Python scalars (\inline{int} and \inline{float}) are supported. For example, see Code Block~\ref{code:parameters}. \inline{Parameters} can be used to conveniently define applied magnetic fields and penetration depths that depend on position, and make it possible to serialize wrapped Python functions for storage or inter-process communication.

@@

Once the layers, films, holes, and abstract regions have been defined, one can generate the computational mesh by calling \inline{Device.make_mesh()}. The region that is meshed is defined by the convex hull of the union of all polygons in the device. Mesh generation is a two step process. First, an initial Delaunay mesh is created using \inline{meshpy}~\cite{Klockner}, a Python interface to Triangle~\cite{shewchuk96b, Shewchuk}, a fast compiled 2D mesh generation tool. Second (and optionally), the mesh can be further optimized using \inline{optimesh}~\cite{nico_schlomer_adam_dobrawy_2021}. The goal of the mesh optimization step is to improve the quality of each triangular element in the mesh, where quality is defined as twice the ratio of the incircle radius to the circumcircle radius (quality $\leq1$, with equality for equilateral triangles). The local density of triangles in the mesh is determined by the density of vertices in the device's polygons and the total number of triangles. Regions where there are many polygon vertices will be meshed more densely than regions with few polygon vertices. If no \inline{optimesh} optimization is done, then every polygon vertex is guaranteed to be a mesh vertex.

@@

Figure X shows a \inline{Device} representing field coil and pickup loop of an actual scanning SQUID sensor. In addition to the field coil and pickup loop, there are superconducting shields that limit the amount of magnetic flux that can penetrate the leads connecting the loops to the rest of the circuit. There are three relevant layers of superconducting films: the base electrode (``BE"), which is furthest from the sample contains the field coil; the first wiring layer (``W1"), which contains the pickup loop and a shield covering the field coil leads; and the second wiring layer (``W2"), which is closest to the sample and contains a shield covering the pickup loop leads. The device also contains a layer and film representing the superconducting sample.

To model a SQUID susceptometry measurement, we first calculate $M_0$, the mutual inductance between the field coil and pickup loop in the absence of the sample. This can be done by temporarily setting the sample layer effective penetration depth to a very large value such that it essentially does not screen the field from the field coil. We then model the field from a known current flowing in the field coil following Section~\ref{section:model:holes} and self-consistently calculate the response of both the sample and the other superconducting layers of the SQUID sensor following Section~\ref{section:model:multilayer}. To ensure that the 2D current distribution in the field coil is approximately uniform (as we would expect for a real applied current), we set the field coil layer effective penetration depth to be greater than the width of the field coil conductor.

@@

@@

\begin{minipage}{\textwidth}
\begin{code}
\begin{minted}[fontsize=\small]{bash}
# Start a ray cluster from the command line, e.g. bash
ray start --head --num=cpus=3
\end{minted}

@@

Maybe demonstrate scaling on Sherlock here.

>>>>

Once the stream function $\mathbf{g}$ is known for the full mesh,
the sheet current flowing in the film can be computed from Eq.~\ref{eq:stream}, the $z$-component of the total field in the plane of the film can be computed
from Eq.~\ref{eq:field_from_kernel_num}, and the full vector magnetic field $\vec{H}(x, y, z)$
at any point in space can be computed from Eqs.~\ref{eq:field_from_kernel} and ~\ref{eq:kernels}.

@@

A \inline{superscreen.Parameter} is a wrapper around a Python function that computes a scalar value as a function of position coordinates ($x$, $y$, and optionally $z$) based on some set of keyword arguments. Addition, subtraction, multiplication, division, and exponentiation between \inline{Parameters}, other \inline{Parameters}, and Python scalars (\inline{int} and \inline{float}) are supported (see Code Block~\ref{code:parameters}). \inline{Parameters} can be used to conveniently define applied magnetic fields and penetration depths that depend on position, and make it possible to serialize wrapped Python functions for storage to disk or inter-process communication.

@@

Once the layers, films, holes, and abstract regions have been defined, one can generate the computational mesh by calling \inline{Device.make_mesh()}. The region that is meshed is defined by the convex hull of the union of all polygons in the device. Mesh generation is a two step process. First, an initial Delaunay mesh is created using \inline{meshpy}~\cite{Klockner}, which is a Python interface to Triangle~\cite{shewchuk96b, Shewchuk}, a fast compiled 2D mesh generation tool. Second (and optionally), the mesh can be further optimized using \inline{optimesh}~\cite{nico_schlomer_adam_dobrawy_2021}. The goal of the mesh optimization step is to improve the quality of each triangular element in the mesh, where quality is defined as twice the ratio of the incircle radius to the circumcircle radius (quality $\leq1$, with equality for equilateral triangles). The local density of triangles in the mesh is determined by the density of vertices in the device's polygons and the total number of triangles. Regions where there are many polygon vertices will be meshed more densely than regions with few polygon vertices. If no \inline{optimesh} optimization is done, then every polygon vertex is guaranteed to be a mesh vertex.

@@

% \begin{figure}[!h]
% \centering
% \begin{subfigure}{.35\textwidth}
%   \centering
%   \includegraphics[width=\linewidth]{examples/images/squid_susceptometry/squid_with_sample_mesh.png}
%   \label{fig:squid_mesh}
%   \caption{}
% \end{subfigure}%
% \hspace{10pt}
% \begin{subfigure}{.5\textwidth}
%   \centering
%   \includegraphics[width=\linewidth]{examples/images/squid_susceptometry/squid_with_sample_M0_convergence.png}
%   \label{fig:squid_convergence}
%   \caption{}
% %   \caption{Fractional change in flux though all polygons vs. solver iteration with a current of $1\,\mathrm{mA}$ flowing in the field coil (\inline{fc}). The mutual inductance $M_0$ is given by the flux through the pickup loop (\inline{pl_hull}) divided by the field coil current.}
% \end{subfigure}%
% \caption{(a): Device polygons and mesh for the SQUID susceptometer model. (b) Fractional change in flux though all polygons vs. solver iteration with a current of $1\,\mathrm{mA}$ flowing in the field coil (\inline{fc}). The mutual inductance $M_0$ is given by the flux through the pickup loop (\inline{pl_hull}) divided by the field coil current.}
% \label{fig:susceptometry}
% \end{figure}

Figure~\ref{fig:susceptometry}(a) shows a \inline{Device} representing field coil and pickup loop of an actual scanning SQUID sensor. In addition to the field coil and pickup loop, there are superconducting shields that limit the amount of magnetic flux that can penetrate the leads connecting the loops to the rest of the circuit (the rest of the circuit is not modeled). There are three relevant layers of superconducting films: the base electrode (``BE"), which is furthest from the sample contains the field coil; the first wiring layer (``W1"), which contains the pickup loop and a shield covering the field coil leads; and the second wiring layer (``W2"), which is closest to the sample and contains a shield covering the pickup loop leads. The device also contains a layer and film representing the superconducting sample.

To model a SQUID susceptometry measurement, we first calculate $M_0$, the mutual inductance between the field coil and pickup loop in the absence of the sample. This can be done by temporarily setting the sample layer effective penetration depth to a very large value such that it essentially does not screen the field from the field coil (in this case, we set $\Lambda = 10^5\,\mu\mathrm{m}$). We then model the field from a known current flowing in the field coil following Section~\ref{section:model:holes} and self-consistently calculate the response of both the sample and the other superconducting layers of the SQUID sensor following Section~\ref{section:model:multilayer}. To ensure that the 2D current distribution in the field coil is approximately uniform (as we would expect for a real applied current), we set the field coil layer effective penetration depth to be greater than the width of the field coil conductor.

@@

% \begin{figure}[!h]
% \centering
% \begin{subfigure}{\textwidth}
%   \centering
%   \includegraphics[width=\linewidth]{examples/images/squid_susceptometry/squid_with_sample_currents_Lambda=1_00__um__z=-1_00__um.png}
% %   \caption{Device polygons and mesh for the SQUID susceptometer model.}
% %   \label{fig:squid_mesh}
% \end{subfigure}%
% \vspace{-15pt}
% \begin{subfigure}{\textwidth}
%   \centering
%   \includegraphics[width=\linewidth]{examples/images/squid_susceptometry/squid_with_sample_currents_Lambda=10_00__um__z=-1_00__um.png}
% %   \caption{Fractional change in flux though all polygons vs. solver iteration with a current of $1\,\mathrm{mA}$ flowing in the field coil (\inline{fc}). The mutual inductance $M_0$ is given by the flux through the pickup loop (\inline{pl_hull}) divided by the field coil current.}
% %   \label{fig:squid_convergence}
% \end{subfigure}%
% \vspace{-15pt}
% \begin{subfigure}{\textwidth}
%   \centering
%   \includegraphics[width=\linewidth]{examples/images/squid_susceptometry/squid_with_sample_currents_Lambda=1_00__um__z=-10_00__um.png}
% %   \caption{Fractional change in flux though all polygons vs. solver iteration with a current of $1\,\mathrm{mA}$ flowing in the field coil (\inline{fc}). The mutual inductance $M_0$ is given by the flux through the pickup loop (\inline{pl_hull}) divided by the field coil current.}
% %   \label{fig:squid_convergence}
% \end{subfigure}%
% \caption{Left: Device polygons and mesh for the SQUID susceptometer model. Right: Fractional change in flux though all polygons vs. solver iteration with a current of $1\,\mathrm{mA}$ flowing in the field coil (\inline{fc}). The mutual inductance $M_0$ is given by the flux through the pickup loop (\inline{pl_hull}) divided by the field coil current.}
% % \label{fig:susceptometry}
% \end{figure}

@@

\begin{minipage}{\textwidth}
\begin{code}
\begin{minted}[fontsize=\small]{bash}
# Start a ray cluster from the command line, e.g. bash
ray start --head --num-cpus=3
\end{minted}

@@
